### 2019-06-04 thesis.tex
Added section about collective processes

\section{Astrophysical plasmas}
\label{sec:astro-plasmas}
The plasma physics branch of Physics is broad. From life-changing
industrial applications like the plasma processing of integrated
circuits - an essential step of the manufacturing process of tiny
integrated circuits -, passing through the development of the
telecommunications via radio-frequency, to day-to-day devices
like fluorescent lamps \cite{bell,gurnett2017,chen}. Another
important application of plasmas on Earth

@@

\chapter{Theoretical framework}
\label{cha:theo-fram}

>>>>

@@

\section{Collective and collisional processes in plasmas}
\label{sec:collec-coll-proc}
In order to understand what collective processes are, one has to
have in mind that a plasma is a many-body system composed mostly
- or completely - of charged particles, that interact with each
other through electromagnetic forces. Due to the long range nature
of the electromagnetic forces, one charge can interact with several
charges at the same time, that will interact with others, and so
on. In such arrangement, the particle motion, at a certain volume
element of the plasma, will be affected not only by the surrounding
environment, but it will also be influenced by the conditions at
distant regions of the system. This nonlocal feature of the plasma
dynamics is called \emph{collective behavior} \cite{chen}.

Collective behavior is a necessary condition for an ionized to be
considered a plasma. As a fundamental characteristic, it occurs in
plasmas that exhibit overall neutrality, the so-called neutral
plasmas, and also in nonneutral plasmas.
